---
title: "Vein Paper Data Processing"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load required libraries.
```{r Loading Packages & Setting Colors, warning=FALSE, message=FALSE}
# Load libraries
library(readxl)
library(tidyr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(gridExtra)
library(paletteer)
library(ggpubr)
library(cowplot)
library(patchwork)
library(png)
library(grid)
library(magick)
library(ggiraph)
library(ggprism)

# Set color palette 
orange1 = paletteer::paletteer_d("NatParksPalettes::Cuyahoga")[2]
orange2 = paletteer::paletteer_d("NatParksPalettes::Cuyahoga")[1]
green1 = paletteer::paletteer_d("NatParksPalettes::IguazuFalls")[2]
green2 = paletteer::paletteer_d("NatParksPalettes::IguazuFalls")[1]
red2 = paletteer::paletteer_d("nationalparkcolors::ArcticGates")[6]
red1 = paletteer::paletteer_d("nationalparkcolors::Saguaro")[2]
blue1 = paletteer::paletteer_d("nationalparkcolors::CraterLake")[1]
blue2 = paletteer::paletteer_d("nationalparkcolors::CraterLake")[5]
lakota1 = paletteer::paletteer_d("MetBrewer::Lakota")[1]
lakota2 = paletteer::paletteer_d("MetBrewer::Lakota")[2]
lakota3 = paletteer::paletteer_d("MetBrewer::Lakota")[3]
my_colors = c(orange1, orange2, green1, green2, red1, red2, blue1, blue2, lakota1, lakota2, lakota3)

# Predefined color indices for the models
model_colors <- c(
    "P93 3mo" = 1,
    "P93 12mo" = 2,
    "P96 3mo" = 3,
    "P96 12mo" = 4,
    "P98 3mo" = 5,
    "P98 12mo" = 6,
    "P104 3mo" = 7,
    "P104 12mo" = 8,
    "3mm" = 9, 
    "6mm" = 10,
    "9mm" = 11
)
```

Define custom functions (not shown in knitted version). These functions take in the following inputs: 

- 'ModelName' is used to attach an identifier to the dataset being processed, (e.g. '"3mm"'). This is a convenient way to change the name that will ultimately appear in figure legends.

- 'ModelData' takes in a dataframe from a *single* model, usually subset from a larger dataframe.

- 'include_errorbar' takes a TRUE/FALSE logical argument. TRUE will include error bars, FALSE will exclude them.

- 'vertical' likewise takes a TRUE/FALSE logical argument. TRUE will stack the plots vertically, while FALSE will arrange the plots in a single row.

- '...' is where the single model datasets are input. This allows you to plot as many or as few models on a single graph as you wish.
```{R Custom Functions for Data Processing and Presentation, echo=FALSE }
# Define function to calculate mean streamline angle and relevant WSS values
# Written to process single model data that has been subsetted from the larger dataset
calculate_model_stats <- function(ModelName, ModelData) {
  library(dplyr)
  
  FlowRates <- unique(ModelData$FlowRate)
  
  # DataFrame to store results
  DataFrame <- data.frame(
    'Flow Rate' = FlowRates,
    'Global Average WSS' = numeric(length(FlowRates)), 
    'Global Average WSS Std' = numeric(length(FlowRates)),
    'Prebend Average WSS' = numeric(length(FlowRates)),
    'Prebend Average WSS Std' = numeric(length(FlowRates)),
    'Prebend Inner WSS' = numeric(length(FlowRates)),
    'Prebend Inner WSS Std' = numeric(length(FlowRates)),
    'Prebend Outer WSS' = numeric(length(FlowRates)),
    'Prebend Outer WSS Std' = numeric(length(FlowRates)),
    'Bend Average WSS' = numeric(length(FlowRates)),
    'Bend Average WSS Std' = numeric(length(FlowRates)),
    'Bend Inner WSS' = numeric(length(FlowRates)),
    'Bend Inner WSS Std' = numeric(length(FlowRates)),
    'Bend Outer WSS' = numeric(length(FlowRates)),
    'Bend Outer WSS Std' = numeric(length(FlowRates)),
    'Postbend Average WSS' = numeric(length(FlowRates)), 
    'Postbend Average WSS Std' = numeric(length(FlowRates)), 
    'Postbend Inner WSS' = numeric(length(FlowRates)),
    'Postbend Inner WSS Std' = numeric(length(FlowRates)),
    'Postbend Outer WSS' = numeric(length(FlowRates)),
    'Postbend Outer WSS Std' = numeric(length(FlowRates)),
    'Prebend Angle' = numeric(length(FlowRates)),
    'Prebend Angle Std' = numeric(length(FlowRates)),
    'Bend Angle' = numeric(length(FlowRates)),
    'Bend Angle Std' = numeric(length(FlowRates)),
    'Postbend Angle' = numeric(length(FlowRates)),
    'Postbend Angle Std' = numeric(length(FlowRates))
  )
  
  for (i in seq_along(FlowRates)) {
    flow_rate <- FlowRates[i]
    
    # Subset data by region and flow rate
    global.subset <- filter(ModelData, FlowRate == flow_rate)
    prebend.subset <- filter(ModelData, Region == "Prebend" & FlowRate == flow_rate)
    prebend.inner <- filter(ModelData, Region == "Prebend" & Wall == "Inner" & FlowRate == flow_rate)
    prebend.outer <- filter(ModelData, Region == "Prebend" & Wall == "Outer" & FlowRate == flow_rate)
    bend.subset <- filter(ModelData, Region == "Bend" & FlowRate == flow_rate)
    bend.inner <- filter(ModelData, Region == "Bend" & Wall == "Inner" & FlowRate == flow_rate)
    bend.outer <- filter(ModelData, Region == "Bend" & Wall == "Outer" & FlowRate == flow_rate)
    postbend.subset <- filter(ModelData, Region == "Postbend" & FlowRate == flow_rate)
    postbend.inner <- filter(ModelData, Region == "Postbend" & Wall == "Inner" & FlowRate == flow_rate)
    postbend.outer <- filter(ModelData, Region == "Postbend" & Wall == "Outer" & FlowRate == flow_rate)
    
    # WSS Calculations
    global.wss <- mean(global.subset$WSS_mean, na.rm = TRUE)
    global.wss.std <- sqrt(mean(global.subset$WSS_var, na.rm = TRUE))
    
    prebend.wss <- mean(prebend.subset$WSS_mean, na.rm = TRUE)
    prebend.wss.std <- sqrt(mean(prebend.subset$WSS_var, na.rm = TRUE))
    prebend.inner.wss <- mean(prebend.inner$WSS_mean, na.rm = TRUE)
    prebend.inner.wss.std <- sqrt(mean(prebend.inner$WSS_var, na.rm = TRUE))
    prebend.outer.wss <- mean(prebend.outer$WSS_mean, na.rm = TRUE)
    prebend.outer.wss.std <- sqrt(mean(prebend.outer$WSS_var, na.rm = TRUE))
    
    bend.wss <- mean(bend.subset$WSS_mean, na.rm = TRUE)
    bend.wss.std <- sqrt(mean(bend.subset$WSS_var, na.rm = TRUE))
    bend.inner.wss <- mean(bend.inner$WSS_mean, na.rm = TRUE)
    bend.inner.wss.std <- sqrt(mean(bend.inner$WSS_var, na.rm = TRUE))
    bend.outer.wss <- mean(bend.outer$WSS_mean, na.rm = TRUE)
    bend.outer.wss.std <- sqrt(mean(bend.outer$WSS_var, na.rm = TRUE))
    
    postbend.wss <- mean(postbend.subset$WSS_mean, na.rm = TRUE)
    postbend.wss.std <- sqrt(mean(postbend.subset$WSS_var, na.rm = TRUE))
    postbend.inner.wss <- mean(postbend.inner$WSS_mean, na.rm = TRUE)
    postbend.inner.wss.std <- sqrt(mean(postbend.inner$WSS_var, na.rm = TRUE))
    postbend.outer.wss <- mean(postbend.outer$WSS_mean, na.rm = TRUE)
    postbend.outer.wss.std <- sqrt(mean(postbend.outer$WSS_var, na.rm = TRUE))
    
    # Angle Calculations
    prebend.angle <- mean(prebend.subset$Angle_mean, na.rm = TRUE)
    prebend.std <- sqrt(mean(prebend.subset$Angle_var, na.rm = TRUE))
    bend.angle <- mean(bend.subset$Angle_mean, na.rm = TRUE)
    bend.std <- sqrt(mean(bend.subset$Angle_var, na.rm = TRUE))
    postbend.angle <- mean(postbend.subset$Angle_mean, na.rm = TRUE)
    postbend.std <- sqrt(mean(postbend.subset$Angle_var, na.rm = TRUE))
    
    # Compile data
    DataFrame[i,] <- c(flow_rate, global.wss, global.wss.std, prebend.wss, prebend.wss.std, prebend.inner.wss, prebend.inner.wss.std, prebend.outer.wss, prebend.outer.wss.std, bend.wss, bend.wss.std, bend.inner.wss, bend.inner.wss.std, bend.outer.wss, bend.outer.wss.std, postbend.wss, postbend.wss.std, postbend.inner.wss, postbend.inner.wss.std, postbend.outer.wss, postbend.outer.wss.std, prebend.angle, prebend.std, bend.angle, bend.std, postbend.angle, postbend.std)
  }
  
  DataFrame$Model <- ModelName
  DataFrame <- as.data.frame(DataFrame)
  return(DataFrame)
}

# Define function to calculate trendline statistics for global WSS values 
calculate_trendline_stats <- function(...) {
  combined_WSS_data <- bind_rows(...)
  models <- unique(combined_WSS_data$Model)

  trends <- data.frame(Model=character(), Slope=numeric(), Intercept=numeric(), R_squared=numeric(), stringsAsFactors=FALSE)
  
  for (model in models) {
    working_data <- filter(combined_WSS_data, Model == model)
    
    lm_model <- lm(Global.Average.WSS ~ Flow.Rate, data=working_data)
    trends <- rbind(trends, data.frame(
      Model = model,
      Slope = coef(lm_model)[2],
      Intercept = coef(lm_model)[1],
      R_squared = summary(lm_model)$r.squared
    ))
  }
  return(trends)
}

# Define function to plot streamline angle v. flow rate, separated by region
create_regional_angle_plot <- function(include_errorbar = FALSE, vertical = TRUE, ymin = 0, ylimit = 90, ...) {
    # Combine input data frames into one
    combined_angle_data <- do.call(rbind, list(...))
    combined_angle_data <- as.data.frame(combined_angle_data)
    
    # Ensure 'Model' is a factor with the correct levels
    model_levels <- names(model_colors)
    combined_angle_data$Model <- factor(combined_angle_data$Model, levels = model_levels)
    combined_angle_data <- droplevels(subset(combined_angle_data, !is.na(Model)))
    
    # Select colors from color palette for plotting
    lookup_colors <- setNames(my_colors, model_levels)
  
    # Filter patient_parameters to only those matching the combined_angle_data
    relevant_parameters <- patient_parameters[patient_parameters$Time_point %in% combined_angle_data$Model, ]
    relevant_parameters$Model <- factor(relevant_parameters$Time_point, levels = model_levels)

    margin_size = 0.15
    ymin = ymin
    h_just = 0.1
    
    # Prebend angle plot
    prebend_angle_plot <- ggplot(combined_angle_data, aes(x = Flow.Rate, y = Prebend.Angle, color = Model)) +
        geom_point(size = 3, shape = 16) +
        scale_color_manual(values = lookup_colors) +
        labs(title = "Prebend", x = "", y = "", color = "Model") +
        theme(text = element_text(size = 14)) +
        ylim(ymin, ylimit) + 
        theme_cowplot() + 
        theme(plot.title = element_text(size = 12, hjust = h_just, vjust = -8, face = "plain")) +
        theme(plot.margin = unit(c(margin_size, margin_size, 0, margin_size), "cm")) + 
        theme(panel.border = element_rect(color = "black", fill = NA, size = 1)) + 
        coord_cartesian(clip = "off") +
        annotation_ticks(sides = "bl", type = "minor", outside = TRUE)+ 
        theme(legend.position = "bottom", legend.justification = "center", legend.box = "horizontal")
  
    # Bend angle plot
    bend_angle_plot <- ggplot(combined_angle_data, aes(x = Flow.Rate, y = Bend.Angle, color = Model)) +
        geom_point(size = 3, shape = 16) +
        scale_color_manual(values = lookup_colors) + 
        guides(shape = "none", color = "none") +
        labs(title = "Bend", x = "", y = "", color = "Model") +
        theme(text = element_text(size = 14)) +
        ylim(ymin, ylimit) + 
        theme_cowplot() + 
        theme(plot.title = element_text(size = 12, hjust = h_just, vjust = -8, face = "plain")) +
        theme(plot.margin = unit(c(margin_size, margin_size, 0, margin_size), "cm")) + 
        theme(panel.border = element_rect(color = "black", fill = NA, size = 0.75))+ 
        coord_cartesian(clip = "off") +
        annotation_ticks(sides = "bl", type = "minor", outside = TRUE)+ 
        theme(legend.position = "bottom", legend.justification = "center", legend.box = "horizontal")
    
    # Postbend angle plot
    postbend_angle_plot <- ggplot(combined_angle_data, aes(x = Flow.Rate, y = Postbend.Angle, color = Model)) +
        geom_point(size = 3, shape = 16) +
        scale_color_manual(values = lookup_colors) + 
        labs(title = "Postbend", x = "", y = "", color = "Model") +
        guides(shape = guide_legend(title = "Wall"), color = guide_legend(title = "Model")) +
        theme(text = element_text(size = 14), legend.position = "bottom") +
        ylim(ymin, ylimit) + 
        theme_cowplot() + 
        theme(plot.title = element_text(size = 12, hjust = h_just, vjust = -8, face = "plain")) +
        theme(plot.margin = unit(c(margin_size, margin_size, 0, margin_size), "cm")) + 
        theme(panel.border = element_rect(color = "black", fill = NA, size = 1))+ 
        coord_cartesian(clip = "off") +
        annotation_ticks(sides = "bl", type = "minor", outside = TRUE) + 
        theme(legend.position = "bottom", legend.justification = "center", legend.box = "horizontal")

    # Add geom_errorbar if include_errorbar is TRUE
    if (include_errorbar) {
        prebend_angle_plot <- prebend_angle_plot +
            geom_errorbar(aes(ymin = Prebend.Angle - Prebend.Angle.Std, ymax = Prebend.Angle + Prebend.Angle.Std), width = 5)
        bend_angle_plot <- bend_angle_plot +
            geom_errorbar(aes(ymin = Bend.Angle - Bend.Angle.Std, ymax = Bend.Angle + Bend.Angle.Std), width = 5)
        postbend_angle_plot <- postbend_angle_plot +
            geom_errorbar(aes(ymin = Postbend.Angle - Postbend.Angle.Std, ymax = Postbend.Angle + Postbend.Angle.Std), width = 5)
    }

    # Conditionally change orientation
    if (vertical) {
        prebend_angle_plot <- prebend_angle_plot + labs(title = "Prebend", x = "", y = "", color = "Model")
        bend_angle_plot <- bend_angle_plot + labs(title = "Bend", x = "", y = "Streamline angle (\u00b0)", color = "Model")
        postbend_angle_plot <- postbend_angle_plot + labs(title = "Postbend", x = "Flow Rate (mL/min)", y = "", color = "Model")
        regional_angle_plot <- ggarrange(prebend_angle_plot, bend_angle_plot, postbend_angle_plot, nrow = 3, common.legend = TRUE, legend = "bottom")
    } else {
        prebend_angle_plot <- prebend_angle_plot + labs(title = "Prebend", x = "", y = "Streamline angle (\u00b0)", color = "Model")
        bend_angle_plot <- bend_angle_plot + labs(title = "Bend", x = "Flow Rate (mL/min)", y = "", color = "Model")
        postbend_angle_plot <- postbend_angle_plot + labs(title = "Postbend", x = "", y = "", color = "Model")
        regional_angle_plot <- ggarrange(prebend_angle_plot, bend_angle_plot, postbend_angle_plot, ncol = 3, common.legend = TRUE, legend = "bottom")
    }

    return(regional_angle_plot)
}


# Define function to plot global WSS v. flow rate
create_global_WSS_plot <- function(include_errorbar = FALSE, include_trendline = FALSE, ...) {
    # Combine input data frames into one
    combined_WSS_data = do.call(rbind, list(...))
    
    # Ensure 'Model' is a factor with the correct levels
    model_levels <- names(model_colors)
    combined_WSS_data$Model <- factor(combined_WSS_data$Model, levels = model_levels)
  
    # Select colors from color palette for plotting
    lookup_colors <- setNames(my_colors, model_levels)
    
    # Create global WSS plot
    global_WSS_plot <- ggplot() +
        geom_point(data=combined_WSS_data, aes(x=Flow.Rate, y=Global.Average.WSS, color=Model), size=2.5, shape=16) + 
        labs(title='',
             x='Flow Rate (mL/min)',
             y='Global Average WSS (mPa)',
             color='Model') +
        scale_color_manual(values = lookup_colors) + 
        theme_cowplot() +
        theme(text = element_text(size=12)) + 
        theme(panel.border = element_rect(color = "black", fill = NA, size = 1)) + 
        theme(legend.position = "bottom", legend.justification = "center")
    
    # Conditionally include error bars
    if (include_errorbar) {
        global_WSS_plot <- global_WSS_plot + geom_errorbar(data=combined_WSS_data, aes(x=Flow.Rate, ymin=(Global.Average.WSS - Global.Average.WSS.Std), ymax=(Global.Average.WSS + Global.Average.WSS.Std), color=Model, width=5))
    }
    # Conditionally include trendlines
    if (include_trendline) {
        global_WSS_plot <- global_WSS_plot + geom_smooth(data=combined_WSS_data, aes(x=Flow.Rate, y=Global.Average.WSS, color=Model), method = "lm", se=FALSE, linetype="dotted")
    }
    return(global_WSS_plot)
}

# Define function to sort angle data into bins
calculate_bins <- function(dataframe) {
  dataframe <- na.omit(dataframe)
  result <- dataframe %>%
    group_by(FlowRate, bin) %>%
    summarise(n = n(), .groups = 'drop') %>%      
    group_by(FlowRate) %>%
    mutate(percentage = n / sum(n) * 100)
  
    all_bins <- c("0-5", "5-15", "15-25", "25-35", "35-45", ">45")
    result$bin <- factor(result$bin, levels = rev(all_bins))
    
    result_ungrouped <- result %>%
      ungroup() %>%
      complete(FlowRate, bin, fill = list(percentage = 0))
  
  return(result_ungrouped)
}

# Define function to created stacked area angle plot
created_stacked_area_angle_plot <- function(data, title, x_label = TRUE, y_label = TRUE) {
  plot <- ggplot(data, aes(x = FlowRate, y = percentage, fill = bin)) +
    geom_area(position = "stack", alpha = 0.6, colour = "black", size = 0.5) +
    theme_cowplot() +
    labs(title = title) +
    guides(fill=guide_legend(title="Angle Bin")) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold"))
  
  if (y_label) {
    plot <- plot + labs(y = "Percentage (%)")
  } else {
    plot <- plot + theme(axis.title.y = element_blank())
  }
  
  if (x_label) {
    plot <- plot + labs(x = "Flow Rate (mL/min)")
  } else {
    plot <- plot + theme(axis.title.x = element_blank())
  }
  
  return(plot)
}

# Define function to identify ROIs that are consistently low WSS
find_low_WSS_zones <- function(model_data, cutoff = 50) {
  bottom_decile <- quantile(model_data$WSS_mean, probs = 0.1)
  
  model_data <- model_data %>%
    mutate(Low_WSS = WSS_mean < bottom_decile) %>%
    group_by(ModelName, Region, Wall, Position)
  
  result <- model_data %>%
    group_by(ModelName, Region, Wall, Position) %>%
    summarise(Pct_Bottom_Decile = mean(Low_WSS, na.rm = TRUE) * 100)
  
  result <- filter(result, Pct_Bottom_Decile >= cutoff)
  
  result$Pct_Bottom_Decile <- round(result$Pct_Bottom_Decile, 1)
  
  print(result)
}
```


Read in Toy Model data:
```{r Reading & Filtering Data}
#Load in spreadsheet containing all toy model data
file_path = "C:/your/file/path/toy_models_full_combined_summary.xlsx"
toy_model_data = read_excel(file_path)


# Stratify data by streamline angle
toy_model_data <- toy_model_data %>%
  mutate(bin = case_when(
    Angle_mean <= 5 ~ "0-5",
    Angle_mean > 5 & Angle_mean <= 15 ~ "5-15",
    Angle_mean > 15 & Angle_mean <= 25 ~ "15-25",
    Angle_mean > 25 & Angle_mean <= 35 ~ "25-35",
    Angle_mean > 35 & Angle_mean <= 45 ~ "35-45",
    Angle_mean > 45 ~ ">45",
    TRUE ~ NA_character_
  ))


#Calculate variances for mean WSS and streamline angle for later calculations
toy_model_data$WSS_var = (toy_model_data$WSS_std)^2
toy_model_data$Angle_var = (toy_model_data$Angle_std)^2

# Filter out rows with low wall coverage to remove poor quality data
toy_model_data <- filter(toy_model_data, WallCoverage > 0.25)

#Separate data by model
toy_3mm_data = filter(toy_model_data, ModelName == "3mm_Toy")
toy_6mm_data = filter(toy_model_data, ModelName == "6mm_Toy")
toy_9mm_data = filter(toy_model_data, ModelName == "9mm_Toy")

#Example to show data structure
head(toy_3mm_data)

# Calculate Model Statistics
toy_3mm = calculate_model_stats("3mm", toy_3mm_data)
toy_6mm = calculate_model_stats("6mm", toy_6mm_data)
toy_9mm = calculate_model_stats("9mm", toy_9mm_data)
```

```{r Global WSS Plot - Toy Models}
# Display trends data frame
global_WSS_plot = create_global_WSS_plot(include_errorbar = TRUE, include_trendline = TRUE, toy_3mm, toy_6mm, toy_9mm)
print(trends)
global_WSS_plot
ggsave(filename = "global_WSS_plot.png", plot=global_WSS_plot, bg="white", height = 2.95, width = 4, units = "in")

# Extract slope, intercept, and R-squared
trends = calculate_trendline_stats(toy_3mm, toy_6mm, toy_9mm)
```

```{r Regional Angle Plot - Toy Models}
# Create regional angle plot for all three toy models
toy_angle_plot = create_regional_angle_plot(include_errorbar = TRUE, vertical = TRUE, ymin = -7 ,ylimit = 40, toy_3mm, toy_6mm, toy_9mm)
toy_angle_plot
ggsave(filename = "toy_angle_plot.png", plot=toy_angle_plot, bg="white", height = 6.25, width = 4, units = "in")
```

Read in Patient Model data:
```{r Load in Patient Model Data}
#Load in spreadsheet containing all patient model data
file_path = "C:/your/file/path/patient_models_combined_summary.xlsx"
patient_model_data = read_excel(file_path)


# Calculate add variance columns
patient_model_data$WSS_var = (patient_model_data$WSS_std)^2
patient_model_data$Angle_var = (patient_model_data$Angle_std)^2

# Filter out rows with low wall coverage to remove poor quality data
patient_model_data <- filter(patient_model_data, WallCoverage > 0.25)

# Stratify data by streamline angle
patient_model_data <- patient_model_data %>%
  mutate(bin = case_when(
    Angle_mean <= 5 ~ "0-5",
    Angle_mean > 5 & Angle_mean <= 15 ~ "5-15",
    Angle_mean > 15 & Angle_mean <= 25 ~ "15-25",
    Angle_mean > 25 & Angle_mean <= 35 ~ "25-35",
    Angle_mean > 35 & Angle_mean <= 45 ~ "35-45",
    Angle_mean > 45 ~ ">45",
    TRUE ~ NA_character_
  ))


# Filter
P104_3mo_data = filter(patient_model_data, ModelName == "P104_3mo")
P104_12mo_data = filter(patient_model_data, ModelName == "P104_12mo")
P96_3mo_data = filter(patient_model_data, ModelName == "P96_3mo")
P96_12mo_data = filter(patient_model_data, ModelName == "P96_12mo")
P93_3mo_data = filter(patient_model_data, ModelName == "P93_3mo")
P93_12mo_data = filter(patient_model_data, ModelName == "P93_12mo")
P98_3mo_data = filter(patient_model_data, ModelName == "P98_3mo")
P98_12mo_data = filter(patient_model_data, ModelName == "P98_12mo")

# Add 'ModelName' Column
P104_12mo_data$ModelName = "P104 12mo"
P104_3mo_data$ModelName = "P104 3mo"
P96_12mo_data$ModelName = "P96 12mo"
P96_3mo_data$ModelName = "P96 3mo"
P93_12mo_data$ModelName = "P93 12mo"
P93_3mo_data$ModelName = "P93 3mo"
P98_12mo_data$ModelName = "P98 12mo"
P98_3mo_data$ModelName = "P98 3mo"
toy_3mm_data$ModelName = "3mm"
toy_6mm_data$ModelName = "6mm"
toy_9mm_data$ModelName = "9mm"

# Process patient data
P104_3mo = calculate_model_stats("P104 3mo", P104_3mo_data)
P104_12mo = calculate_model_stats("P104 12mo", P104_12mo_data)
P96_3mo = calculate_model_stats("P96 3mo", P96_3mo_data)
P96_12mo = calculate_model_stats("P96 12mo", P96_12mo_data)
P93_3mo = calculate_model_stats("P93 3mo", P93_3mo_data)
P93_12mo = calculate_model_stats("P93 12mo", P93_12mo_data)
P98_3mo = calculate_model_stats("P98 3mo", P98_3mo_data)
P98_12mo = calculate_model_stats("P98 12mo", P98_12mo_data)
```

```{r Patient Global WSS Plots}
P104_global_WSS <- create_global_WSS_plot(include_errorbar = TRUE, include_trendline = TRUE, P104_12mo, P104_3mo)
ggsave(filename = "P104_global_WSS_plot.png", plot=P104_global_WSS, bg="white", height = 4, width = 4.75, units = "in")

P96_global_WSS <- create_global_WSS_plot(include_errorbar = TRUE, include_trendline = TRUE, P96_3mo,P96_12mo, toy_6mm)
ggsave(filename = "P96_global_WSS_plot.png", plot=P96_global_WSS, bg="white", height = 3, width = 4.75, units = "in")

P98_global_WSS <- create_global_WSS_plot(include_errorbar = TRUE, include_trendline = TRUE, P98_3mo,P98_12mo)
ggsave(filename = "P98_global_WSS_plot.png", plot=P98_global_WSS, bg="white", height = 4, width = 4.75, units = "in")

P93_global_WSS <- create_global_WSS_plot(include_errorbar = TRUE, include_trendline = TRUE, P93_3mo,P93_12mo)
ggsave(filename = "P93_global_WSS_plot.png", plot=P93_global_WSS, bg="white", height = 4, width = 4.75, units = "in")

# Extract slope, intercept, and R-squared
calculate_trendline_stats(P104_3mo, P104_12mo, P96_3mo, P96_12mo, P93_3mo, P93_12mo, P98_3mo, P98_12mo)
```

```{r Patient Regional Angle Plots}
P104_regional_angles <- create_regional_angle_plot(ymin = -6, ylimit = 70, include_errorbar = TRUE, vertical = FALSE,include_vlines = FALSE, P104_3mo, P104_12mo)
ggsave(filename = "P104_regional_angles.png", plot = last_plot(), bg="white", height = 4, width = 9, units = "in")

P96_regional_angles <- create_regional_angle_plot(ymin = -6, ylimit = 55, include_errorbar = TRUE, vertical = TRUE,include_vlines = FALSE, P96_3mo, P96_12mo, toy_6mm)
save_plot(filename = "P96_regional_angles.png", plot = last_plot(), bg="white", base_height = 6.5, base_width = 3.75, units = "in")

P98_regional_angles <- create_regional_angle_plot(ymin = -7, ylimit = 60, include_errorbar = TRUE, vertical = FALSE,include_vlines = FALSE, P98_3mo, P98_12mo)
ggsave(filename = "P98_regional_angles.png", plot = last_plot(), bg="white", height = 4, width = 9, units = "in")

P93_regional_angles <- create_regional_angle_plot(ymin = -5, ylimit = 55, include_errorbar = TRUE, vertical = FALSE,include_vlines = FALSE, P93_3mo, P93_12mo)
ggsave(filename = "P93_regional_angles.png", plot = last_plot(), bg="white", height = 4, width = 9, units = "in")
```

```{r Calculating Bins for All Models}
P93_3mo_bins <- calculate_bins(P93_3mo_data)
P93_12mo_bins <- calculate_bins(P93_12mo_data)
P96_3mo_bins <- calculate_bins(P96_3mo_data)
P96_12mo_bins <- calculate_bins(P96_12mo_data)
P98_3mo_bins <- calculate_bins(P98_3mo_data)
P98_12mo_bins <- calculate_bins(P98_12mo_data)
P104_3mo_bins <- calculate_bins(P104_3mo_data)
P104_12mo_bins <- calculate_bins(P104_12mo_data)

toy_3mm_bins <- calculate_bins(toy_3mm_data)
toy_6mm_bins <- calculate_bins(toy_6mm_data)
toy_9mm_bins <- calculate_bins(toy_9mm_data)
```

```{r Creating Stacked Area Plots}
P93_3mo_stacked <- created_stacked_area_angle_plot(P93_3mo_bins, title = "P93 3mo", y_label = TRUE)
ggsave(filename = "P93_3mo_stacked_angles.png", plot=last_plot(), bg="white", height = 4.29, width = 5, units = "in")

P93_12mo_stacked <- created_stacked_area_angle_plot(P93_12mo_bins, title = "P93 12mo", y_label = TRUE)
ggsave(filename = "P93_12mo_stacked_angles.png", plot=last_plot(), bg="white", height = 4.29, width = 5, units = "in")

P96_3mo_stacked <- created_stacked_area_angle_plot(P96_3mo_bins, title = "P96 3mo", y_label = FALSE)
P96_12mo_stacked <- created_stacked_area_angle_plot(P96_12mo_bins, title = "P96 12mo", y_label = FALSE, x_label = FALSE)

P98_3mo_stacked <- created_stacked_area_angle_plot(P98_3mo_bins, title = "P98 3mo", y_label = TRUE)
ggsave(filename = "P98_3mo_stacked_angles.png", plot=last_plot(), bg="white", height = 4.29, width = 5, units = "in")

P98_12mo_stacked <- created_stacked_area_angle_plot(P98_12mo_bins, title = "P98 12mo", y_label = TRUE)
ggsave(filename = "P98_12mo_stacked_angles.png", plot=last_plot(), bg="white", height = 4.29, width = 5, units = "in")

P104_3mo_stacked <- created_stacked_area_angle_plot(P104_3mo_bins, title = "P104 3mo", y_label = TRUE)
ggsave(filename = "P104_3mo_stacked_angles.png", plot=last_plot(), bg="white", height = 4.29, width = 5, units = "in")
P104_12mo_stacked <- created_stacked_area_angle_plot(P104_12mo_bins, title = "P104 12mo", y_label = TRUE)
ggsave(filename = "P104_12mo_stacked_angles.png", plot=last_plot(), bg="white", height = 4.29, width = 5, units = "in")



P93_stacked <- ggarrange(P93_3mo_stacked, P93_12mo_stacked, ncol = 2, common.legend = TRUE, legend = "right")
ggsave(filename = "P93_stacked_angles.png", plot=last_plot(), bg="white", height = 4, width = 7.5, units = "in")

P96_stacked <- ggarrange(P96_3mo_stacked, P96_12mo_stacked, common.legend = TRUE, legend = "right")
ggsave(filename = "P96_stacked_angles.png", plot=last_plot(), bg="white", height = 4, width = 7.5, units = "in")

P98_stacked <- ggarrange(P98_3mo_stacked, P98_12mo_stacked, ncol = 2, common.legend = TRUE, legend = "right")
ggsave(filename = "P98_stacked_angles.png", plot=last_plot(), bg="white", height = 4, width = 7.5, units = "in")

P104_stacked <- ggarrange(P104_3mo_stacked, P104_12mo_stacked, ncol = 2, common.legend = TRUE, legend = "right")
ggsave(filename = "P104_stacked_angles.png", plot=last_plot(), bg="white", height = 4, width = 7.5, units = "in")

toy_3mm_stacked <- created_stacked_area_angle_plot(toy_3mm_bins, title = "3 mm Toy", y_label = TRUE)
toy_3mm_stacked <- toy_3mm_stacked + theme(legend.position = "none")
ggsave(filename = "toy_3mm_stacked.png", plot=last_plot(), bg="white", height = 4, width = 4, units = "in")

toy_6mm_stacked <- created_stacked_area_angle_plot(toy_6mm_bins, title = "6 mm Toy", y_label = TRUE, x_label = FALSE)
ggsave(filename = "toy_6mm_stacked.png", plot=last_plot(), bg="white", height = 4, width = 4, units = "in")

toy_9mm_stacked <- created_stacked_area_angle_plot(toy_9mm_bins, title = "9 mm Toy", y_label = FALSE)
ggsave(filename = "toy_9mm_stacked.png", plot=last_plot(), bg="white", height = 4, width = 4, units = "in")

fig3_stacked_plot <- ggarrange(toy_6mm_stacked, P96_3mo_stacked, P96_12mo_stacked, ncol = 3, common.legend = TRUE, legend = "right", align = "h")
ggsave(filename = "fig3_stacked_plot.png", plot=last_plot(), bg="white", height = 3.2, width = 9.83, units = "in")


fig2_stacked_plot <- ggarrange(toy_3mm_stacked, toy_9mm_stacked, ncol = 2, common.legend = TRUE, legend = "right", align = "h")
ggsave(filename = "fig2_stacked_plot.png", plot=last_plot(), bg="white", height = 2.5, width = 11, units = "in")
```

```{r Identifying Consistently Low WSS Zones}
find_low_WSS_zones(P93_3mo_data)
find_low_WSS_zones(P93_12mo_data)
find_low_WSS_zones(P96_3mo_data)
find_low_WSS_zones(P96_12mo_data)
find_low_WSS_zones(P98_3mo_data)
find_low_WSS_zones(P98_12mo_data)
find_low_WSS_zones(P104_3mo_data)
find_low_WSS_zones(P104_12mo_data)

find_low_WSS_zones(toy_3mm_data)
find_low_WSS_zones(toy_6mm_data)
find_low_WSS_zones(toy_9mm_data)
```
